Nanophotonic Computational Design

### 2013-02-24 defense/pres3.tex
Closer...

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\newcommand{\nextpage}{\vfill\newpage}

\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

@@

\newcommand{\smallfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=6.5cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\medfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=10cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\bigfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=12cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

@@

\begin{document}
\setlength{\parskip}{0cm}
\maketitle
\begin{itemize} \itemsep -1pt
\I  Introduction
\I  Summary
\I  Incremental results
\I  Final result
\EI

% \BIT \itemsep -1pt
% \item motivation
% \item theory
% \item results
% \EIT

@@

\I  On-chip optical components are currently designed
    by tuning a small number of design parameters
\smallfig{integrated_circuit}
\pause
\I  Our idea: Design using \emph{all} available parameters
    \BI If successful, full-parameter design \emph{guarantees} better devices 
    \I  i.e. We can do better by using \emph{all} the design parameters \EI

@@

% \I  The full parameter space for nanophotonic design is \emph{vast}
% \I  How big is the full design space for nanophotonic devices?
\I The number of available design parameters for nanophotonic devices
    is \emph{enormous}
\smallfig{des_complexity}
\pause
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
    \BI $2^{225} = 67$-digit number, uncountable \EI
\pause
\I  Realization: Hand-tuning won't work for full-parameter design
\nextpage

\I  Realization: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description enables the design of \emph{everything} 
    \EI
\pause
\I  Assumption: Design-by-description can actually be made to work
\pause
\I  Our goal: Make it work!

\oursection{Summary}
\smallfig{takeaway}
\I  Our work: Designed 3D linear nanophotonic devices
    \BI Using the full parameter space
    \I  Using design-by-description \EI
\nextpage

@@

\I  Our approach:
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause

@@

\oursection{Given a field, can we find its device/structure?}
\I  Answer: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!) \\
    \stepwise{
    \begin{align*} 
    \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E &= 
        -i \omega J \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\\
    \step{\omega^2 \epsilon E &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\omega^2 E \epsilon &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\epsilon &= (\nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J)/ \omega^2 E} 
    \end{align*}
    (Reminder, $\epsilon = \vec{\epsilon}(r), E=\vec{E}(r), J = \vec{J}(r)$)
\step{
\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
}

@@

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    }
    \step{
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }

@@

\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\I  Choose canonical 1D cavity field for $x$
\I  Solve for $z$ (structure) and check design fidelity with simulation
\smallfig{1d_leastsquares}
\pause
\I  Result: Perfect performance, but unmanufacturable structure ($z$)
\nextpage

@@

\myfig{1d_regularized_12}{11.5}
\I  Unfortunately, regularization on $z$ decreases performance 
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

@@

\I  How to overcome the apparent trade-off between manufacturability ($z$)
    and performance ($x$)?
\pause
\I  Realized that there do exist some $x$ (fields)
    which result from manufacturable $z$ (structures)
    \BI These can be produced via simulation
    \I  However, it's not useful to ask the user to choose such $x$ \EI
\pause
\I  Therefore, a \emph{useful} tool would optimize for \emph{both} $x$ and $z$
\nextpage

\oursection{Iterative design of nanophotonic devices}
\I  New algorithm: Iteratively solve for $x$ (field) and $z$ (structure)
    \pause
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2 
    \end{align*}
    \pause
\I  Takes advantage of the \emph{bi-linearity} of the physics residual
    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
\nextpage

@@

\smallfig{1d_alternate}
\I  Iterative strategy produces $z$ (structure) that 
    \BI is better behaved
    \I  more accurately produces $x$ \EI
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

@@

\smallfig{1d_hardlimit}
\I  Well-behaved, manufacturable $z$ (structure)
\I  Final $x$ (field) accurately reproduced
\I  Majority of elements of $z$ are fortuitously at one limit or the other!
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\I  Can be used to create 2D resonators
\smallfig{2d_circ}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\I  3D resonators can be designed using a ``2.5D'' approximation
\smallfig{25d_circ}
\footnotetext{J. Lu, S. Boyd, J. Vuckovic, Optics Express (2011)}
\nextpage

\oursection{Objective-first design of linear devices}
\stepwise{
\I  Next realization: for linear components, 
    only certain elements of $x$ (field) matter
\step{\BI Specifically, the elements of $x$ at the input/output ports \EI}
\step{
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 \\
    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
        & z_\text{min} \le z \le z_\text{max}
    \end{align*}
}
\step{
\I  Instead of regularization term, we force the elements of $x$
    at the boundary to be equal to the ideal case ($\hat{x}$)}
}
\nextpage

@@

\I  Coupler to wide, low-index waveguide
\medfig{ob1_wg}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\I  Coupler from fundamental to second-order waveguide mode
\medfig{ob1_wg2}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\oursection{Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  Goal: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\footnotetext{D. A. B. Miller, ``All linear optical devices are mode converters,''
    Optics Express (2012)}
\nextpage

\I  Problem: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
    \BI Millions of variables
    \I  Famously ill-conditioned 
    \I  No known commercial \emph{solvers} that can handle arbitrary structures \EI
\pause
\smallfig{wonseok}
\I  Fortunately, Wonseok had already solved this problem
\footnotetext{W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,'' J. Comp. Phys. (2012)}

\oursection{Maxwell: Light-simulation supercomputer}
\I  Partnered with Wonseok to develop a cloud-based electromagnetic solver 
    using Amazon Web Services 
    \BI GPU-accelerated implementation of Wonseok's algorithm
    \I  Cluster scales automatically to tens of nodes \EI
\smallfig{maxwell}
\nextpage

\I  Scalable
    \BI Far outstrips computing clusters such as Teragrid
    \I  Can perform multiple solves in parallel, on a single Matlab instance 
    \I  All computation is performed externally (in the cloud) \EI
\pause
\I  Easy to use
    \BI Installs with a single Matlab command
    \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI
\pause
\I  The key technological enabler in achieving 3D design
\nextpage

\oursection{3D design: problem statement}
\stepwise{
    \step{
\begin{align*}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align*}
    }
\step{
\I  $M$ modes with $N_i$ monitored output modes each}
    \step{\BI $b_i$ is the input excitation for each mode
    \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI}
}
\nextpage

\medfig{3D_wgc_te}
\I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
\I  Output mode is enforced using overlap integrals
    ($c_{ij}\T x_i$ or $\int \hat{E_{ij}} E$)
\nextpage

% \oursection{Structure of 3D designs}
% \I  250 nm silicon slab surrounded by silica

@@

\medfig{3D_wgc_tm}
\nextpage

@@

\medfig{3D_spl_modal}
\nextpage

@@

\medfig{3D_spl_tetm}
\nextpage

@@

\medfig{3D_spl_wdm}
\nextpage

@@

\medfig{3D_hub_3x3}
\nextpage

@@

\medfig{3D_hub_4x4}
\nextpage

@@

\medfig{3D_hub_2x2x2}
\nextpage

@@

\medfig{3D_fib_te}
\nextpage

@@

\medfig{3D_fib_pol}
\nextpage

@@

\medfig{3D_fib_wdm}
\nextpage

>>>>

\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\newcommand{\nextpage}{\vfill\newpage}
\newcommand{\bold}{\textbf}
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

@@

\newcommand{\smallfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=6.5cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\medfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=10cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\bigfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[height=12cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\threeDfig}[1]{
    \begin{figure}[!h]
    \centerline{\includegraphics[width=20cm]{fig/#1.jpg}}
    \end{figure}
}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}

@@

\begin{document}
\setlength{\parskip}{0cm}
\maketitle
% \begin{itemize} \itemsep -1pt
% \I  Introduction
% \I  Summary
% \I  Incremental results
% \I  Final result
% \EI
\nextpage

\I  On-chip optical components are currently designed
    by tuning a small number of design parameters
\smallfig{integrated_circuit}
\pause
\I  \bold{Our idea}: Design using \emph{all} available parameters
    \BI If successful, full-parameter design \emph{guarantees} better devices 
    \I  i.e. We can do better by using \emph{all} the design parameters \EI

@@

% \I  The full parameter space for nanophotonic design is \emph{vast}
% \I  How big is the full design space for nanophotonic devices?
\I The number of available design parameters for nanophotonic devices
    is \emph{enormous}
\smallfig{des_complexity}
\pause
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
    \BI $2^{225} = 67$-digit number, uncountable \EI
\pause
\I  \bold{Realization}: Hand-tuning won't work for full-parameter design
\nextpage

\I  \bold{Realization}: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description enables the design of \emph{everything} 
    \EI
\pause
\I  \bold{Assumption}: Design-by-description can actually be made to work
\pause
\I  \bold{Our goal}: Make it work!

@@

\oursection{Summary}
\smallfig{takeaway}
\I  Designed 3D linear nanophotonic devices
    \BI Using the full parameter space
    \I  Using design-by-description \EI
\nextpage

@@

\I  \bold{Our approach}:
    \BI applying (convex) optimization techniques (math)
    \I  to the area of nanophotonics (physics)
    \I  and implementing in software (programming) \EI
\pause

@@

\oursection{Given a field, can we find its device/structure?}
\I  \bold{Answer}: Yes, given $E$ we \emph{can} solve for $\epsilon$ (trivial!) \\
    \stepwise{
    \begin{align*} 
    \nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E &= 
        -i \omega J \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\\
    \step{\omega^2 \epsilon E &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\omega^2 E \epsilon &= \nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J }\\
    \step{\epsilon &= (\nabla\times\mu_0^{-1}\nabla\times E + 
        i \omega J)/ \omega^2 E} 
    \end{align*}
    (Reminder, $\epsilon = \vec{\epsilon}(r), E=\vec{E}(r), J = \vec{J}(r)$)
\step{
\I  Solving for $\epsilon$ actually way faster than simulation (solving for $E$)!
}

@@

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    }
    \step{
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  \bold{Key}: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }

@@

\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\I  Choose canonical 1D cavity field for $x$
\I  Solve for $z$ (structure) and check design fidelity with simulation
\smallfig{1d_leastsquares}
\pause
\I  \bold{Result}: Perfect performance, but unmanufacturable structure ($z$)
\nextpage

@@

\I  \bold{Regularized direct solve result}: decreased performance
\myfig{1d_regularized_12}{11.5}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

@@

\I  \bold{Problem}: How to overcome the apparent trade-off 
    between manufacturability ($z$) and performance ($x$)?
\pause
\I  Realized that there do exist some $x$ (fields)
    which result from manufacturable $z$ (structures)
    \BI These can be produced via simulation
    \I  However, it's not useful to ask the user to choose such $x$ \EI
\pause
\I  Therefore, a \emph{useful} tool would optimize for \emph{both} $x$ and $z$
\nextpage

\oursection{Iterative design of nanophotonic devices}
\I  \bold{New algorithm}: Iteratively solve for $x$ (field) and $z$ (structure)
    \pause
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_0\|z - z_\text{prev}\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_1\|x - x_\text{prev}\|^2 
    \end{align*}
    \pause
\I  Takes advantage of the \emph{bi-linearity} of the physics residual
    \BI Jointly solving for $x$ and $z$ is a non-convex problem \EI
\nextpage

@@

\I  \bold{Result of iterative strategy}: $z$ (structure) that 
    \BI is better behaved
    \I  more accurately produces $x$ \EI
\smallfig{1d_alternate}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

@@

\I  \bold{Result of iterative design with hard constraints on $z$}:
\BI Well-behaved, manufacturable $z$ (structure)
\I  Final $x$ (field) accurately reproduced
\I  Majority of elements of $z$ are fortuitously at one limit or the other \EI
\smallfig{1d_hardlimit}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\I  \bold{Extension}: Iterative design can be used to create 2D resonators as well
\smallfig{2d_circ}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2010)}
\nextpage

\I  \bold{Extension}: 3D resonators can be designed using a ``2.5D'' approximation
\smallfig{25d_circ}
\myfig{25d_approx}{4}
\footnotetext{J. Lu, S. Boyd, J. Vuckovic, Optics Express (2011)}
\nextpage

\oursection{Objective-first design of linear devices}
\stepwise{
\I  Next realization: for linear components, 
    only certain elements of $x$ (field) matter
\step{\BI Specifically, the elements of $x$ at the input/output ports \EI}
\step{
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 \\
    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
        & z_\text{min} \le z \le z_\text{max}
    \end{align*}
}
\step{
\I  Instead of regularization term, we force the elements of $x$
    at the boundary to be equal to the ideal case ($\hat{x}$)}
\footnotetext{D. A. B. Miller, ``All linear optical devices are mode converters,''
    Optics Express (2012)}
}
\nextpage

@@

\I  \bold{2D objective-first result}: Coupler to wide, low-index waveguide
    \BI Efficiency: 99.8\%
    \I  Footprint: 1.5 square vacuum wavelengths \EI
\medfig{ob1_wg}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\I  \bold{2D objective-first result}: Coupler to second-order waveguide mode
    \BI Efficiency: 98.0\%
    \I  Footprint: 1.5 square vacuum wavelengths \EI
\medfig{ob1_wg2}
\footnotetext{J. Lu, J. Vuckovic, Optics Express (2012)}
\nextpage

\oursection{Final result: Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  \bold{Goal}: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Design-by-description (objective-first)
    \I  Uses the full parameter space
    \I  High efficiency
    \I  Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\nextpage

\I  \bold{Problem}: Did not know how to solve $A(z)x - b = 0$ (simulation) in 3D
    \BI Millions of variables
    \I  Famously ill-conditioned 
    \I  No known commercial \emph{solvers} that can handle arbitrary structures \EI
\pause
\smallfig{wonseok}
\I  Fortunately, Wonseok Shin (Fan group) had already solved this problem
\footnotetext{W. Shin, S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,'' J. Comp. Phys. (2012)}

\oursection{Maxwell: Light-simulation supercomputer}
\I  Partnered with Wonseok to develop electromagnetic solver-as-a-service 
    \BI GPU-accelerated implementation of Wonseok's algorithm
    \I  Cluster scales automatically in the cloud (Amazon Web Services)\EI
\smallfig{maxwell}
\nextpage

\I  Accuracy 
    \BI Solves the frequency domain problem directly 
    \I  Allows for precise input excitation and output monitoring \EI
\pause
\I  Scalability
    \BI Far outstrips computing clusters such as Teragrid
    \I  Can perform multiple solves in parallel, from a single Matlab instance 
    \I  All computation is performed externally (in the cloud) \EI
\pause
\I  Ease-of-use
    \BI Installs with a single Matlab command
    \I  Solves completed with a single Matlab command: \verb+maxwell(...);+ \EI
\pause
\I  \bold{The key technological enabler in achieving 3D design}
\nextpage

\oursection{Final result: Problem statement}
\stepwise{
    \step{
\begin{align*}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align*}
    }
\step{
\I  $M$ modes with $N_i$ monitored output modes each}
    \step{\BI $b_i$ is the input excitation for each mode
    \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI}
}
\nextpage

\I  Problem statement in physics language
\threeDfig{3Db_wgc_te}
\I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
\I  Output mode is enforced using overlap integrals
    ($c_{ij}\T x_i$ or $\int \hat{E_{ij}} E$)
\nextpage

\oursection{Final result: Method}
\footnotetext{S. Boyd et al, Foundations and Trends in Machine Learning (2011)}
\I  Objective-first problem solved using 
    alternating directions method of moments (ADMM)
    \BI Addition of dual variable greatly accelerates convergence \EI
\pause
\I  After objective-first solution
    \BI $z$ is converted to boundary parameterization for manufacturability
    \I  Steepest-descent used in secondary optimization step \EI
\pause
\I  Basic device structure:
    \BI 250 nm silicon slab surrounded by silica
    \I  Permittivity: 12.25 (Si), 2.25 (SiO$_2$) \EI
\nextpage

\oursection{Result 1: Mode converter (TE)}
\threeDfig{3Db_wgc_te}
% \I  Converts from fundamental TE (in-plane polarized) mode to 
%     second-order mode
\I  Performance description at output waveguide:
    \BI Power in second-order mode: 90\% to 100\%
    \I  Power in first-order mode: 0\% to 1\% (rejection) \EI
\nextpage

@@

\threeDfig{3Db_wgc_tm}
\nextpage

@@

\threeDfig{3Db_spl_modal}
\nextpage

@@

\threeDfig{3Db_spl_tetm}
\nextpage

@@

\threeDfig{3Db_spl_wdm}
\nextpage

@@

\threeDfig{3Db_hub_3x3}
\nextpage

@@

\threeDfig{3Db_hub_4x4}
\nextpage

@@

\threeDfig{3Db_hub_2x2x2}
\nextpage

@@

\threeDfig{3Db_fib_te}
\nextpage

@@

\threeDfig{3Db_fib_pol}
\nextpage

@@

\threeDfig{3Db_fib_wdm}
\nextpage
